Icicle: fuse your queries

### 2016-04-06 2016fhpc/Main.tex
ok

\title{Icicle: a single-pass query language}

\authorinfo{
  Amos Robinson$^\dagger$$^\ddagger$
  \and Ben Lippmeier$^\dagger$
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{amosr,benl@cse.unsw.edu.au}
  }
  \shortstack{
    $^\ddagger$Ambiata      \\
    Big data and shit       \\[2pt]
    \textsf{amos.robinson@ambiata.com}
  }
}

@@

\begin{abstract}
When streaming a large amount of data, simply iterating over the data may take hours.
In this case, the difference between a query that takes one iteration and a query that takes multiple iterations must be very explicit.
For many purposes, limiting queries to a single pass is sufficient.
We introduce a type system based on modality types to enforce this single pass restriction.
By using an appropriate intermediate language we guarantee fusion between queries on the same table, before extracting efficient single-loop C code.
\end{abstract}

@@

\input{section/01-Introduction.tex}
\input{section/02-Source.tex}
\input{section/03-Types.tex}
\input{section/04-Core.tex}
\input{section/05-Generation.tex}
\input{section/06-Conclusion.tex}

\input{section/XX-Related-DataFlow.tex}
% \input{figures/Source-Type-Modal.tex}

>>>>

\title{Icicle: fuse your queries}

\authorinfo{
  Amos Robinson$^\dagger$$^\ddagger$
  \and Ben Lippmeier$^\dagger$
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{amosr,benl@cse.unsw.edu.au}
  }
  \shortstack{
    $^\ddagger$Ambiata      \\
    Grow with data          \\[2pt]
    \textsf{amos.robinson@ambiata.com}
  }
}

@@

\begin{abstract}
When streaming a large amount of data, simply iterating over the data may take hours.
If multiple queries are to be performed, it is important that work is not duplicated.
Queries that can be performed together must be performed in the same iteration.
We introduce a simple streaming language for computing queries in a single-pass over the data.
By using an appropriate intermediate language we guarantee fusion between queries on the same input streams, before extracting efficient C code.
\end{abstract}

@@

\input{section/01-Introduction.tex}
\input{section/02-Core.tex}
